### 2023-03-08 manuscript.tex
Fixing 10.5281/zenodo.6097109 [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/db4ebdb09871e3ca3db2086b8fabfe614cc5ba56.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/db4ebdb09871e3ca3db2086b8fabfe614cc5ba56/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/4367119918

This manuscript
(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/2ba66415ee4d5e69b7890e54bec942747e76e441/}{permalink})
was automatically generated
from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/2ba66415ee4d5e69b7890e54bec942747e76e441}{SORTEE-Github-Hackathon/manuscript@2ba6641}
on March 8, 2023.

@@

\leavevmode\vadjust pre{\hypertarget{ref-GQj3c17f}{}}%
Hudgins, E. (2022). \emph{emmajhudgins/UStreedamage: publication release} (accepted) {[}Computer software{]}. Zenodo. \url{https://doi.org/10.5281/zenodo.6097109}

>>>>

This manuscript
(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/db4ebdb09871e3ca3db2086b8fabfe614cc5ba56/}{permalink})
was automatically generated
from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/db4ebdb09871e3ca3db2086b8fabfe614cc5ba56}{SORTEE-Github-Hackathon/manuscript@db4ebdb}
on March 8, 2023.

@@

\leavevmode\vadjust pre{\hypertarget{ref-GQj3c17f}{}}%
Hudgins, E. (2022). \emph{Data and code for 'Hotspots of pest‐induced US urban tree death, 2020--2050', published in Journal of Applied Ecology} (published) {[}Computer software{]}. Zenodo. \url{https://doi.org/10.5281/zenodo.6097109}
